\documentclass[../main.tex]{subfiles}

\begin{document}

\section{Conclusion and Future Work}
This work introduces AutoLibra, a new paradigm for agent evaluation, one of
the first works to explore adaptable trajectory-derived evaluation heuristics,
offering substantial advantages in agent training over traditional end-to-end
evaluation. We find that this framework is generalizable to a diverse range of agent
tasks, provides new insights into agent behaviors, and identifies strong optimization
targets for agent improvement. There are a few directions for further extending
and applying this framework.
(1) \textbf{Behavior-centric evaluation} AutoLibra leads a \emph{paradigm shift}
from end-to-end agent evaluation (analogous to ``integration tests'' in software
development) to evaluation with granular metrics that measure agents' concrete behaviors
(analogous to ``unit tests''). Future work can study whether this process can be
improved through better human-AI collaboration.
(2) \textbf{Sub-trajectory feedback from humans} In AutoLibra, we label each
trajectory with one piece of feedback, and ground it into the agents' concrete
behavior which is at the sub-trajectory level. In the future, researchers can
let users directly give feedback for one or multiple steps in the trajectory, which
should lead to better feedback grounding results. Similarly, user feedback can be
collected during the interaction instead of after the agent has completed the tasks,
which is a more user-friendly way to gather high quality feedback data.
(3) \textbf{Wider exploration of agent improvement methods} In this paper, we only
explored non-parametric for agent improvement to show the utility of AutoLibra. Future work can use AutoLibra to provide dense rewards for individual
steps, and use reinforcement learning to train agents with these dense rewards.

\end{document}